\documentclass[10pt, a4paper]{article}

\usepackage[a4paper, top=1.1cm, bottom=1.1cm, left=2.0cm, right=2.0cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{array}
\usepackage{hyperref}
\usepackage{setspace}

\definecolor{rust}{HTML}{8B3A2F}
\definecolor{charcoal}{HTML}{1A1A1A}
\definecolor{dgrey}{HTML}{2D2D2D}
\definecolor{mgrey}{HTML}{666666}
\definecolor{lgrey}{HTML}{AAAAAA}

\hypersetup{colorlinks=false, hidelinks}
\pagestyle{empty}

\setlength{\parskip}{3pt}
\setlength{\parindent}{0pt}

\titleformat{\section}
  {\normalsize\rmfamily\bfseries\color{charcoal}}
  {}{0em}{}
  [\vspace{1pt}{\color{rust}\titlerule[0.5pt]}\vspace{2pt}]
\titlespacing{\section}{0pt}{8pt}{3pt}

\setlist[itemize]{
  label={\textcolor{mgrey}{\small$\bullet$}},
  leftmargin=1.1em,
  itemsep=0pt,
  topsep=1pt,
  parsep=0pt,
  partopsep=0pt
}

\newcommand{\entry}[3]{%
  \vspace{3pt}
  \noindent
  \textbf{\color{charcoal}#1}\hfill{\color{mgrey}\small #3}\\[-2pt]
  {\color{rust}\itshape\small #2}
  \vspace{1pt}
}

\begin{document}

% NAME
{\fontsize{26pt}{30pt}\selectfont\rmfamily\bfseries\color{charcoal} Archie Robertson}

\vspace{3pt}
{\color{lgrey}\hrule height 0.4pt}
\vspace{2pt}
{\small\color{mgrey}
  archie@robertsons.com
  \quad\textcolor{lgrey}{|}
  \quad 07495 791 527
  \quad\textcolor{lgrey}{|}
  \quad Aberdeen, Scotland
}
\vspace{2pt}

% PROFILE
\section{Profile}

\begin{itemize}
  \item Third-year Economics student at St.\ Andrews with a good grounding in economic theory, statistics, and financial mathematics.
  \item Pick up technical tools quickly --- have used Python, Java, and \LaTeX{} throughout my degree.
  \item Four years of youth coaching and hospitality work over summers have driven me to work well in a team and stay organised when it gets busy.
  \item Joining the Breakaways Hillwalking Society committee as Trip Secretary next year.
\end{itemize}

% EDUCATION
\section{Education}

\entry{BSc Economics}{University of St.\ Andrews, Scotland}{Sep 2022 -- Present (Expected Jun 2027)}
\begin{itemize}
  \item Modules include Microeconomics, Macroeconomics, Statistics, and Mathematics for Economics.
  \item Also completed modules in Object-Oriented Programming and Unix-Based Systems alongside the core economics curriculum.
  \item Joining the Breakaways Hillwalking Society committee as Trip Secretary (2025--26), responsible for planning and organising society trips.
\end{itemize}

\entry{Scottish Highers}{Cults Academy, Aberdeen}{2021}
\begin{itemize}
  \item Mathematics: A \enspace Physics: A \enspace Computing: A \enspace Physical Education: A \enspace Chemistry: B
\end{itemize}

% WORK EXPERIENCE
\section{Work Experience}

\entry{Kitchen Porter}{Parx Caf\'{e}, Aberdeen}{Summer 2025}
\begin{itemize}
  \item Responsible for early morning dishwashing and food preparation, ensuring the kitchen was fully operational ahead of service.
  \item Worked in a compact, high-pressure kitchen environment --- the caf\'{e} ran at full capacity most days, requiring focus and efficiency throughout each shift.
  \item Developed the ability to work quickly and methodically in a confined space, maintaining standards under sustained demand.
\end{itemize}

\entry{Youth Sports Coach}{Ian Wilson Soccer Coaching (IWSC), Aberdeen}{Jun 2020 -- Aug 2024}
\begin{itemize}
  \item Ran coaching sessions for groups of up to 20 children at different skill levels --- planned each session in advance and adapted on the day depending on how things were going.
  \item Had to communicate clearly with both the children and their parents and manage a group with very different personalities and abilities.
\end{itemize}

\entry{Kitchen Porter}{Kippie Lodge, Aberdeen}{Jun 2021 -- Aug 2024}
\begin{itemize}
  \item Worked every summer in a busy kitchen --- kept things running smoothly during service, helped with prep, and maintained a clean and organised workspace.
  \item Good for staying focused and keeping pace when things get hectic.
\end{itemize}

% SKILLS
\section{Skills}

\vspace{2pt}
\begin{tabular}{@{}p{2.8cm} l@{}}
  \textbf{Programming}  & Python, Java, \LaTeX{}, Unix / Bash \\[3pt]
  \textbf{Quantitative} & Statistics, data analysis, financial mathematics \\[3pt]
  \textbf{Interests}    & Economics, hillwalking, golf, computer science \\
\end{tabular}

% CERTIFICATIONS
\section{Certifications}

\vspace{2pt}
\begin{tabularx}{\textwidth}{@{}X r@{}}
  Caledonia North Rugby Development Youth Coaching Award & {\color{mgrey}2021} \\[3pt]
  PVG (Protecting Vulnerable Groups) Member --- \#2107 0159 8561 2431 & {\color{mgrey}2023} \\
\end{tabularx}

\vfill

{\color{lgrey}\hrule height 0.4pt}
\vspace{2pt}
{\small\color{lgrey} References available upon request}

\end{document}